Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-21 paper/paper.tex
minor change to simu part

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ from at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (details see Supplementary
Section S7). Similar to the KCl system discussed earlier, the salt
rejection was only observed in the positive $V_{\mathrm{G}}$
regime. The degree of salt rejection deceases with the salt valance;
for example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our simulations,
in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
the same setups in simulations (\Fig{} \ref{fig:6}b). The calculated
$\xi_{\mathrm{max}}$ values are quantitatively compared with
experiments (\Fig{} \ref{fig:6}c), and the same trend is
observed. Indeed, because the Debye screening length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). We notice that without
any fitting parameters, our theory can predict the experimental values
reasonably well. In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of salt diffusivity is
negligible. This finding also explains the concentration dependence of
$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.

\section{Conclusion}
\label{sec:consl}

In summary, we have
presented a comparative experimental and modeling study on macroscopic
salt rejection through a sheet of large-area porous graphene under
electrostatic gating. We show that due to a small quantum capacitance
of double layer graphene, the graphene surface potential is
considerably lower than the applied gate voltage. As a result, the
subtle redistribution of the electrochemical potentials create new
pathways for ionic transport, which in turn lead to a considerably
degree of salt rejection. We report a high degree of salt rejection at
$V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 80\%, based on our
experiments and theoretical predictions, respectively. We demonstrate
that the observed salt rejection positively correlates with the Debye
screening length that nonlinearly modulates the graphene surface
potential and charge density. The experimental results and fundamental
principles presented here open an avenue towards realization of
atomically thin 2D porous membranes for advanced separation process in
electrolyte solutions.

@@

\textbf{Graphene synthesis}: Graphene was grown in a cold-wall,
low-pressure chemical vapor deposition system (BM 4 inch, Aixtron SE)
on surface-pretreated copper foil (Alfa Aesar N$^{o}$ 46986). Synthesis was
carried out at 950 $^{\circ}$C for 3 min using ethylene after 30 min of
hydrogen/argon annealing. A first graphene layer was subsequently
transferred to a second one to yield double layer graphene using a
PMMA transfer method. A glass slide was used as the support for
subsequent patterning of the graphene, PMMA was removed using acetone
ultrasonication and subsequent isopropanol (IPA) rinsing. The entire
process is described in detail in Ref. \citenum{Choi_2018}.

\vspace{1em}
\noindent
\textbf{Graphene patterning and transfer to PCTE}: Spherical block copolymer
(s-BCP) based patterning has enabled the manufacturing of perforated
graphene membranes having pores in the range of 10 nm to 50 nm on
average up to wafer-scale\cite{Choi_2018}. In brief, s-BCP
(polystyrene-block-polymethylmethacrylate, PS-b-PMMA, 195-b-20,
Polymer Source Inc, Canada, 1 weight\% in anhydrous toluene) is spun
from solution and thermally annealed at 220 $^{\circ}$C for 6 h in
vacuum. Microphase separation of s-BCP leads to distinct phases: the
minor phase will form spheres (PMMA) and the major phase will form the
matrix (PS). Oxygen plasma (8 , 100 W, 25 mTorr, Oxford Instruments
plc) removes the top layer PS from the PMMA spheres, which are
subsequentially etched in glacial acetic acid to form a porous etch
mask directly on top of the double layer graphene. Anisotropic etching
using oxygen beam milling (10 s, 100 mA, 600 V acceleration voltage,
Oxford IonFab 600) leads to perforation of the underlying graphene
through the porous PS mask. Polymer residues are removed by thermal
annealing in hydrogen:argon (9:1) at 400 $^{\circ}$C. The patterned
graphene is transferred to PCTE membranes (hydrophobic, 400 nm pores,
from Sterlitech) by baking the PCTE briefly to the perforated graphene
at 180 $^{\circ}$C followed by a lift-off etch in buffered
hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A schematic
of the process is shown in \Fig{} S1.

>>>>

Finally, we examine other salt species and compare the degree of salt
rejection between experiments and simulations. \Fig{} \ref{fig:6}a
presents the measured salt rejection $\xi$ as a function of
$V_{\mathrm{G}}$ at $c_{0}$ = 0.1 mM, for the seven salt species
considered here, including NaCl, LiCl, KCl, MgSO$_{4}$, CaCl$_{2}$,
K$_{2}$SO$_{4}$, and K$_{3}$[Fe(CN)$_{6}$] (Supplementary
Section S7). Similar to the KCl system discussed earlier, the salt
rejection is more pronounced in the positive $V_{\mathrm{G}}$
regime. The degree of salt rejection deceases with the salt valance;
for example, the measured $\xi$ values at $V_{\mathrm{G}}$ = 1.25 V
decreases from $>$ 0.5 for monovalent NaCl to -0.04 for multivalent
K$_{3}$[Fe(CN)$_{6}$]. This observation is endorsed by our simulations,
in which we calculate $\xi$ as a function of $V_{\mathrm{g}}$ using
the same simulation setups(\Fig{} \ref{fig:6}b). The calculated
$\xi_{\mathrm{max}}$ values are quantitatively compared with
experiments (\Fig{} \ref{fig:6}c), and the same trend is
observed. Indeed, because the Debye screening length
$\lambda_{\mathrm{D}}$ decreases with the salt valence, the graphene
surface potential appears to decrease in the multivalent salt systems,
thereby reducing $\xi$ (see \Fig{} \ref{fig:5}b). The calculated and
experimental $\xi_{\mathrm{max}}$ as a function of
$\lambda_{\mathrm{D}}$ are consequently plotted, for the seven salt
species considered here (\Fig{} \ref{fig:6}d). We notice that without
any fitting parameters, our theory can predict the experimental values
reasonably well. In addition, the
$\xi_{\mathrm{max}}-\lambda_{\mathrm{D}}$ dependence is approximately
linear, suggesting that the effect of salt diffusivity is
negligible. This finding also explains the concentration dependence of
$\xi_{\mathrm{max}}$ observed in \Fig{} \ref{fig:2}d, as
$\lambda_{\mathrm{D}} \propto c_{0}^{-0.5}$.

In summary, we have presented a comparative experimental and modeling
study on macroscopic salt rejection through a sheet of large-area
porous graphene under electrostatic gating. We show that due to a
small quantum capacitance of atomically-thin graphene, the graphene
surface potential is considerably lower than the applied gate
voltage. As a result, the subtle redistribution of the electrochemical
potentials create new pathways for ionic transport, which in turn lead
to a considerably degree of salt rejection. We report a high degree of
salt rejection at $V_{\mathrm{G}}$ = 1.25 V of up to 55\% and 85\%,
based on our experiments and theoretical predictions, respectively. We
demonstrate that the observed salt rejection positively correlates
with the Debye screening length that nonlinearly modulates the
graphene surface potential and charge density. The experimental
results and fundamental principles presented here open an avenue
towards realization of atomically thin 2D porous membranes for
advanced separation process in electrolyte solutions.

@@

\textbf{Graphene synthesis}: Graphene was grown in a cold-wall,
low-pressure chemical vapor deposition system (BM 4 inch, Aixtron SE)
on surface-pretreated copper foil (Alfa Aesar No. 46986). Synthesis was
carried out at 950 $^{\circ}$C for 3 min using ethylene after 30 min of
hydrogen/argon annealing. A first graphene layer was subsequently
transferred to a second one to yield double layer graphene using a
PMMA transfer method. A glass slide was used as the support for
subsequent patterning of the graphene, PMMA was removed using acetone
ultrasonication and subsequent isopropanol (IPA) rinsing. The entire
process is described in detail in Ref. \citenum{Choi_2018}.

\vspace{1em}
\noindent
\textbf{Graphene patterning and transfer to PCTE}: Spherical block
copolymer (s-BCP) based patterning has enabled the manufacturing of
perforated graphene membranes having pores in the range of 10 nm to 50
nm on average up to wafer-scale\cite{Choi_2018}. In brief, s-BCP
(polystyrene-block-polymethylmethacrylate, PS-b-PMMA, 195-b-20,
Polymer Source Inc, Canada, 1 weight\% in anhydrous toluene) is
spin-coated from solution and thermally annealed at 220 $^{\circ}$C
for 6 h in vacuum. Microphase separation of s-BCP leads to distinct
phases: the minor phase will form spheres (PMMA) and the major phase
will form the matrix (PS). Oxygen plasma (8 , 100 W, 25 mTorr, Oxford
Instruments plc) removes the top layer PS from the PMMA spheres, which
are subsequentially etched in glacial acetic acid to form a porous
etch mask directly on top of the double layer graphene. Anisotropic
etching using oxygen beam milling (10 s, 100 mA, 600 V acceleration
voltage, Oxford IonFab 600) leads to perforation of the underlying
graphene through the porous PS mask. Polymer residues are removed by
thermal annealing in hydrogen:argon (9:1) at 400 $^{\circ}$C. The
patterned graphene is transferred to PCTE membranes (hydrophobic, 400
nm pores, from Sterlitech) by baking the PCTE briefly to the
perforated graphene at 180 $^{\circ}$C followed by a lift-off etch in
buffered hydrofluoric acid (BHF) as described by\cite{Choi_2018}. A
schematic of the process is shown in \Fig{} S1.
